Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-16 paper/sheaf_lics.tex
test of username
added a section on the eli-mono fact. system

In this section, we review some basic definitions in homotopy type
theory that are central in our formalization but not specific to
sheafification. 
%
Section~\ref{ssec:hott} introduces the notion of homotopy types and
classifying objects as defined in~\cite{sets_in_hott}.
%
Section~\ref{sec:colim-homot-type} introduces the notion of colimits
in homotopy type theory. 
%
And Section~\ref{sec:giraud-ax} defines a particular case of
Giraud-Rezk-Lurie axioms on higher topoi that we need in the
definition of sheafification.
%
The definition of Section~\ref{ssec:hott} are part of the Coq library
available at \url{https://github.com/HoTT/HoTT}, while other definitions
and theorems are specific to our formalization.

@@

@@

Let $T : \Type_{n+1}$. We define $\square T$ as the image of
$\modal^T \circ \{\cdot\}_T$, as in
$$\xymatrix{
  T \ar[r]^{\{\cdot\}_T} \ar[d]_{\mu_T} & \Type_n^T \ar[d]^{\modal^T} \\
  \square T \ar[r]& \left( \Type_n^\modal \right)^T
}, $$
where $\{\cdot\}_T$ is the singleton map $\lambda (t:T),~\lambda
(t':T),~t=t'$.
\nt{parler du système de factorization et HoTT book}
In type theory words, 
\begin{align*}
\square T &= \im (\lambda~t:T,~\lambda~ t',~ \modal (t = t')) \\
          &= \sum_{u:T \to \Type_n^\modal} \left\| \sum_{a:X} 
            (\lambda t,~\modal (a=t)) = u\right\|
\end{align*}

>>>>

In this section, we review some basic definitions in homotopy type
theory that are central in our formalization but not specific to
sheafification. 
%
Section~\ref{ssec:hott} introduces the notion of homotopy types and
classifying objects as defined in~\cite{sets_in_hott}.
%
Section~\ref{sec:epi-mono-fact} presents the usual epi-mono
factorization system in the light of homotopy type theory.
%
Section~\ref{sec:colim-homot-type} introduces the notion of colimits
in homotopy type theory. 
%
And Section~\ref{sec:giraud-ax} defines a particular case of
Giraud-Rezk-Lurie axioms on higher topoi that we need in the
definition of sheafification.
%
The definition of Section~\ref{ssec:hott} are part of the Coq library
available at \url{https://github.com/HoTT/HoTT}, while other definitions
and theorems are specific to our formalization.

@@

\subsection{The epi-mono Factorization System}
\label{sec:epi-mono-fact}

\nt{define the image here, with (-1)-truncated and (-1)-connected
  factorization system}

@@

Let $T : \Type_{n+1}$. We define $\square T$ as the image (see
Section~\ref{sec:epi-mono-fact}) of
$\modal^T \circ \{\cdot\}_T$, as in
$$\xymatrix{
  T \ar[r]^{\{\cdot\}_T} \ar[d]_{\mu_T} & \Type_n^T \ar[d]^{\modal^T} \\
  \square T \ar[r]& \left( \Type_n^\modal \right)^T
}, $$
where $\{\cdot\}_T$ is the singleton map $\lambda (t:T),~\lambda
(t':T),~t=t'$.
\nt{parler du système de factorization}
In type theory words, 
\begin{align*}
\square T &= \im (\lambda~t:T,~\lambda~ t',~ \modal (t = t')) \\
          &= \sum_{u:T \to \Type_n^\modal} \left\| \sum_{a:X} 
            (\lambda t,~\modal (a=t)) = u\right\|
\end{align*}
